Conversion from forest to agriculture in the Brazilian Amazon from 1985 to 2021

### 2022-12-22 manuscript/manuscript.Rmd
Small fixes.

Cnversions from forest to agriculture can be found in almost every region in the Amazon, but is mostly concentrated in clusters, specially in the south and east of the biome, in the states of Mato Grosso, Pará and Maranhão (Figure \@ref(fig:map-plot)).

@@

In 2006, the Brazilian Association of Vegetable Oil Industries (BIOVE) and the National Association of Cereal Exporters (ANEC) committed to avoid commercialization of soybean grains harvested from areas deforested after 2008, known as the soy moratorium.
The soy moratorium is considered to have contributed to the decline of the deforestation directly related to soybean expansion [@Paim2021; @Amaral2021; @Heilmayr2020; @Kastens2017]. Our estimates of conversions show a decrease of deforested areas after 2008, where it reached minimal values (Figure @ref(fig:transbar-plot).a). After 2006, agriculture establishment over deforested primary forests suffered a decrease, the low rates of agriculture establishment stayed relatively stable until 2012, where a steep increase occurred. However, the new primary forest areas being occupied by agriculture were mainly over areas that were cleared before 2008 (Figure @ref(fig:transbar-plot).b), which is the last year of deforestation tolerated by the soy moratorium. The period between 2006 and 2010 is also considered as a turnover point, known as the decoupling of deforestation and soybean production, where the total production (total weight of grains) was not as dependent on agriculture expansion as before [@Macedo2012]. However, the observed increase of soybean establishment after 2012 shows that soybean expansion did not halt after the soy moratorium nor after periods of high soybean productivity. Instead of halt expansion, producers started to expand over areas cleared many years ago (70 % of the conversions took more than 10 years), which may still have indirect impacts on deforestation increase over distant areas [@Arima2011; @Gollnow2018; @Silva2021]. Expansion of agricultural areas also occurred over cleared areas of secondary forests in 2012, but with an important amount of fast conversions (Figure @ref(fig:transbar-plot).d). The causes of the increase of agricultural establishment areas over primary and secondary forests can be numerous, and one main driver was the approval of a new Forest Code, in 2012, which is considered to have undermined the environmental protection of forests [@Kroger2017; @Pereira2019], since it opened the possibility of amnesty for illegally deforested areas [@Schielein2018; @Santanna2021; @Filho2014], and the possible reduction of legal reserve area [@Freitas2018].

>>>>

Conversions from forest to agriculture can be found in almost every region in the Amazon, but is mostly concentrated in clusters, specially in the south and east of the biome, in the states of Mato Grosso, Pará and Maranhão (Figure \@ref(fig:map-plot)).

@@

In 2006, the Brazilian Association of Vegetable Oil Industries (BIOVE) and the National Association of Cereal Exporters (ANEC) committed to avoid commercialization of soybean grains harvested from areas deforested after 2008, known as the soy moratorium.
The soy moratorium is considered to have contributed to the decline of the deforestation directly related to soybean expansion [@Paim2021; @Amaral2021; @Heilmayr2020; @Kastens2017].
Our estimates of conversions show a decrease of deforested areas after 2008, where it reached minimal values (Figure \@ref(fig:transbar-plot).a).
After 2006, agriculture establishment over deforested primary forests suffered a decrease, the low rates of agriculture establishment stayed relatively stable until 2012, where a steep increase occurred.
However, the new primary forest areas being occupied by agriculture were mainly over areas that were cleared before 2008 (Figure \@ref(fig:transbar-plot).b), which is the last year of deforestation tolerated by the soy moratorium.
The period between 2006 and 2010 is also considered as a turnover point, known as the decoupling of deforestation and soybean production, where the total production (total weight of grains) was not as dependent on agriculture expansion as before [@Macedo2012].
However, the observed increase of soybean establishment after 2012 shows that soybean expansion did not halt after the soy moratorium nor after periods of high soybean productivity.
Instead of halt expansion, producers started to expand over areas cleared many years ago (70 % of the conversions took more than 10 years), which may still have indirect impacts on deforestation increase over distant areas [@Arima2011; @Gollnow2018; @Silva2021].
Expansion of agricultural areas also occurred over cleared areas of secondary forests in 2012, but with an important amount of fast conversions (Figure \@ref(fig:transbar-plot).d).
The causes of the increase of agricultural establishment areas over primary and secondary forests can be numerous, and one main driver was the approval of a new Forest Code, in 2012, which is considered to have undermined the environmental protection of forests [@Kroger2017; @Pereira2019], since it opened the possibility of amnesty for illegally deforested areas [@Schielein2018; @Santanna2021; @Filho2014], and the possible reduction of legal reserve area [@Freitas2018].

### 2022-12-22 manuscript/manuscript.tex
Small fixes.

Cnversions from forest to agriculture can be found in almost every region in the Amazon, but is mostly concentrated in clusters, specially in the south and east of the biome, in the states of Mato Grosso, Pará and Maranhão (Figure \ref{fig:map-plot}).

@@

In 2006, the Brazilian Association of Vegetable Oil Industries (BIOVE) and the National Association of Cereal Exporters (ANEC) committed to avoid commercialization of soybean grains harvested from areas deforested after 2008, known as the soy moratorium.
The soy moratorium is considered to have contributed to the decline of the deforestation directly related to soybean expansion \citep{Paim2021, Amaral2021, Heilmayr2020, Kastens2017}. Our estimates of conversions show a decrease of deforested areas after 2008, where it reached minimal values (Figure \citet{ref}(fig:transbar-plot).a). After 2006, agriculture establishment over deforested primary forests suffered a decrease, the low rates of agriculture establishment stayed relatively stable until 2012, where a steep increase occurred. However, the new primary forest areas being occupied by agriculture were mainly over areas that were cleared before 2008 (Figure \citet{ref}(fig:transbar-plot).b), which is the last year of deforestation tolerated by the soy moratorium. The period between 2006 and 2010 is also considered as a turnover point, known as the decoupling of deforestation and soybean production, where the total production (total weight of grains) was not as dependent on agriculture expansion as before \citep{Macedo2012}. However, the observed increase of soybean establishment after 2012 shows that soybean expansion did not halt after the soy moratorium nor after periods of high soybean productivity. Instead of halt expansion, producers started to expand over areas cleared many years ago (70 \% of the conversions took more than 10 years), which may still have indirect impacts on deforestation increase over distant areas \citep{Arima2011, Gollnow2018, Silva2021}. Expansion of agricultural areas also occurred over cleared areas of secondary forests in 2012, but with an important amount of fast conversions (Figure \citet{ref}(fig:transbar-plot).d). The causes of the increase of agricultural establishment areas over primary and secondary forests can be numerous, and one main driver was the approval of a new Forest Code, in 2012, which is considered to have undermined the environmental protection of forests \citep{Kroger2017, Pereira2019}, since it opened the possibility of amnesty for illegally deforested areas \citep{Schielein2018, Santanna2021, Filho2014}, and the possible reduction of legal reserve area \citep{Freitas2018}.

>>>>

Conversions from forest to agriculture can be found in almost every region in the Amazon, but is mostly concentrated in clusters, specially in the south and east of the biome, in the states of Mato Grosso, Pará and Maranhão (Figure \ref{fig:map-plot}).

@@

In 2006, the Brazilian Association of Vegetable Oil Industries (BIOVE) and the National Association of Cereal Exporters (ANEC) committed to avoid commercialization of soybean grains harvested from areas deforested after 2008, known as the soy moratorium.
The soy moratorium is considered to have contributed to the decline of the deforestation directly related to soybean expansion \citep{Paim2021, Amaral2021, Heilmayr2020, Kastens2017}.
Our estimates of conversions show a decrease of deforested areas after 2008, where it reached minimal values (Figure \ref{fig:transbar-plot}.a).
After 2006, agriculture establishment over deforested primary forests suffered a decrease, the low rates of agriculture establishment stayed relatively stable until 2012, where a steep increase occurred.
However, the new primary forest areas being occupied by agriculture were mainly over areas that were cleared before 2008 (Figure \ref{fig:transbar-plot}.b), which is the last year of deforestation tolerated by the soy moratorium.
The period between 2006 and 2010 is also considered as a turnover point, known as the decoupling of deforestation and soybean production, where the total production (total weight of grains) was not as dependent on agriculture expansion as before \citep{Macedo2012}.
However, the observed increase of soybean establishment after 2012 shows that soybean expansion did not halt after the soy moratorium nor after periods of high soybean productivity.
Instead of halt expansion, producers started to expand over areas cleared many years ago (70 \% of the conversions took more than 10 years), which may still have indirect impacts on deforestation increase over distant areas \citep{Arima2011, Gollnow2018, Silva2021}.
Expansion of agricultural areas also occurred over cleared areas of secondary forests in 2012, but with an important amount of fast conversions (Figure \ref{fig:transbar-plot}.d).
The causes of the increase of agricultural establishment areas over primary and secondary forests can be numerous, and one main driver was the approval of a new Forest Code, in 2012, which is considered to have undermined the environmental protection of forests \citep{Kroger2017, Pereira2019}, since it opened the possibility of amnesty for illegally deforested areas \citep{Schielein2018, Santanna2021, Filho2014}, and the possible reduction of legal reserve area \citep{Freitas2018}.
